Estimating the socio-environmental impacts of car substitution by bicycle and public transit using open tools

### 2023-09-26 paper/PaperTRA/PaperTRA.Rmd
Add PCT content

<!-- Robin: include here a paragraph about pct, and how biclar adds up -->
**(RL)** The methods of Propensity to Cycle Tool  
adding up an intermodality scenario to estimate cycling potential to public transit interfaces.

>>>>

*biclar* builds on the Propensity to Cycle Tool (PCT), a web application and research project funded by the UK's Department for Transport in 2015 which launched nationally in 2017 as part of the government's Cycling and Walking Investment Strategy.
The PCT initially used only origin-destination data for commuting trips as the basis of estimates of cycling potential at zone, route and route network levels [@Lovelace2017].

### 2023-09-26 paper/PaperTRA/PaperTRA.tex
Add PCT content

\maketitle              % typeset the header of the contribution
%
\begin{abstract}
In metropolitan areas, car trips can be replaced by a combination of
public transit and cycling for the first-and-last mile. This paper
estimates the potential for cycling + public transit (PT) as a
substitute for car trips in the Lisbon metropolitan area and assesses
its socio-environmental impacts using open data and open source tools. A
decision support tool that facilitates the design and development of a
metropolitan cycling network was developed (\emph{biclaR}). A scenario
of intermodality introduced, and its socio-environmental impacts were
assessed using the \emph{HEAT for Cycling} and the \emph{HEAT as a
Service} tools. The impacts of shifting car trips to PT were also
estimated and monetized. The results indicate that 20\% of the current
trips can be made with the bicycle + PT combination. Shifting to cycling
for the first-and-last mile can reduce annual CO\textsubscript{2}eq
emissions from 6,000 tons/day, and the 10-year socio-environmental
benefits account from €230 million. For the PT leg, the transfer from
car avoids of at least 8,500 tons of CO\textsubscript{2}eq emissions per
year. The information on socio-economic benefits can support
policymakers in prioritizing interventions to reduce the reliance on
individual motorized transportation and effectively communicate their
decisions.

@@

According to the latest mobility survey conducted in 2018 {[}1{]}, the
LMA registered a total of 5.3 million daily trips, with only 0.5\% by
bicycle. Car modal share was 58.4\%, while PT accounted for 15.5\%. The
number of intra-municipal trips - with origin and destination in the
same municipality - amounts to 3.5 million trips, exceeding the number
of inter-municipal trips (1.8 million trips) - involving travel between
different municipalities. Cars and public transport are the most used
modes for intercity trips, with cars being the predominant choice for
all journeys.

To achieve the cycling targets set by the Portuguese national cycling
strategy for 2025 and 2030 (4\% and 10\%, respectively) {[}2{]}, the
Lisbon's Metropolitan Department of Transport introduced
\emph{biclaR}\footnote{see
  \href{https://biclar.tmlmobilidade.pt/}{biclar.tmlmobilidade.pt}}, a
decision support tool that facilitates the design and development of a
metropolitan cycling network {[}3{]}.

\textbf{(RL)} The methods of Propensity to Cycle Tool\\
adding up an intermodality scenario to estimate cycling potential to
public transit interfaces.

@@

\hypertarget{assessing-socio-environmental-benefits}{%
\subsection{Assessing socio-environmental
benefits}\label{assessing-socio-environmental-benefits}}

Socio-environmental impacts were assessed using the HEAT for Cycling and
the HEAT as a Service\footnote{see
  \url{https://github.com/HEAT-WHO/HEAT_heatr_api}} tools, from the WHO.
Additionally, we estimate the impacts of shifting car trips to PT for
the second leg of the journey with EMEP/EEA's COPERT methodology and
monetize them with the EU Guide to cost-benefit analysis.

Como referido na introdução, a ferramenta biclaR pretende estimar os
impactes sociais e ambientais associados ao potencial ciclável dos
vários cenários analisados. O horizonte temporal considerado para esta
análise foi o curto prazo (i.e., 1 ano) e o longo prazo (i.e., 10 anos).
Os impactes foram avaliados para cada cenário e para diferentes escalas
territoriais:

@@

>>>>

\maketitle              % typeset the header of the contribution
%
\begin{abstract}
A high proportion of car trips can be replaced by a combination of
public transit and cycling for the first-and-last mile. This paper
estimates the potential for cycling combined with public transit (PT) as
a substitute for car trips in the Lisbon metropolitan area and assesses
its socio-environmental impacts using open data and open source tools. A
decision support tool that facilitates the design and development of a
metropolitan cycling network was developed (\emph{biclaR}). The social
and environmental impacts were assessed using the \emph{HEAT for
Cycling} and the \emph{HEAT as a Service} tools. The impacts of shifting
car trips to PT were also estimated and monetized. The results indicate
that 20\% of car trips could switch to the bicycle + PT combination.
Shifting to cycling for the first-and-last mile stages can reduce annual
CO\textsubscript{2}eq emissions from 6,000 tons/day, with benefits over
10 years of €230 million. For the PT leg, the transfer from car avoids
of at least 8,500 tons of CO\textsubscript{2}eq emissions per year. This
evidence can support policymakers to prioritize interventions that
reduce the reliance on private motor vehicles.

@@

According to the latest mobility survey conducted in 2018 {[}1{]}, the
LMA registered a total of 5.3 million daily trips, with only 0.5\% by
bicycle. Car modal share was 58.4\%, while PT accounted for 15.5\%. The
number of intra-municipal trips --- with origin and destination in the
same municipality --- amounts to 3.5 million trips. This exceeds the
number of inter-municipal trips (1.8 million trips), involving travel
between different municipalities. Cars and public transport are the most
used modes for intercity trips, with cars being the predominant choice
for all journeys.

To achieve the cycling targets set by the Portuguese national cycling
strategy for 2025 and 2030 (4\% and 10\%, respectively) {[}2{]}, the
Lisbon's Metropolitan Department of Transport introduced
\emph{biclaR}\footnote{See
  \href{https://biclar.tmlmobilidade.pt/}{biclar.tmlmobilidade.pt}}, a
decision support tool that facilitates the design and development of a
metropolitan cycling network {[}3{]}.

\emph{biclar} builds on the Propensity to Cycle Tool (PCT), a web
application and research project funded by the UK's Department for
Transport in 2015 which launched nationally in 2017 as part of the
government's Cycling and Walking Investment Strategy. The PCT initially
used only origin-destination data for commuting trips as the basis of
estimates of cycling potential at zone, route and route network levels
{[}\textbf{Lovelace2017?}{]}.

@@

\hypertarget{assessing-socio-environmental-benefits---continue-from-here}{%
\subsection{Assessing socio-environmental benefits - CONTINUE FROM
HERE}\label{assessing-socio-environmental-benefits---continue-from-here}}

Socio-environmental impacts were estimated for a short term time horizon
(i.e., one year) and the long term (i.e., ten years). using the HEAT for
Cycling and the HEAT as a Service\footnote{see
  \url{https://github.com/HEAT-WHO/HEAT_heatr_api}} tools, from the WHO.

Os impactes foram avaliados para cada cenário e para diferentes escalas
territoriais:

@@

Additionally, we estimate the impacts of shifting car trips to PT for
the second leg of the journey with EMEP/EEA's COPERT methodology and
monetize them with the EU Guide to cost-benefit analysis.
